### 2014-10-13 PrivacyProtection-2014-09-09.tex
Deleted "Excessive data mining" (Commented Out)

The Act's definition of''personal data" covers any data that can be used to identify a living individual.
Anonymised or aggregated data is not regulated by the Act, providing the anonymisation or aggregation has not been done in a reversible way.
Individuals can be identified by various means including their name and address, telephone number or Email address.
The Act applies only to data which is held, or intended to be held, on computers (`equipment operating automatically in response to instructions given for that purpose'), or held in a `relevant filing system'.

In some cases even a paper address book can be classified as a `relevant filing system', for example diaries used to support commercial activities such as a salesperson's diary.

@@

%\paragraph{Excessive Data Mining}
%
%\subparagraph{1 Privacy of the Person private''} \cite{1}. Here we are
%concerned wi the personal physiological and psychological p and  This privacy is threat...f \textbf{body characteristics}weight, height,, dna,\ldots) or
%depression emph therapists or other doctors) \textbf{can beevealed orii and emph+Gov project collects sensor data from mobile devices
%(accellerometer, location, \ldots). By a...g \emph{human activityecognition (emph)} techniques we could detect certain movement patterns
%we know the position with of indiviual citizens with a sufficientccurancy, and the Live+Gov project is only applied to a destinct urban
%area. So we could link HAR data with the yellow pages, filter for
%medical specialists and limit the possibilities of pathologic
%conditions. But even without HAR data we could determine a likelihood
%for certain conplaints. Frequent vistits to the dentist does not imply
%healthy teeth.

%\subparagraph{2 Privacy of Behaviour and Action}
%
%\emph{``This type is also concerned with the `protection against
%disclosure of personal matters' through behaviour''}
%\cite{1}. This type is concered with religous
%practices, sexaul habits, political activities, etc. revealed through
%observation. For the Live+Gov project this type is related to t is recirded by default and by linking it to maps a and li phone books those *``personal matters*" could be
%disclosed by frequently visited places (c...s, brothels, party headuaters, \emph).
%
%communications' either electronic or face-to-face'' \cite{1}. This type
%is threatened if we intrude the secrecy of correspondence, posts and
%telecommunications, personal direct communication or right to free
%discussion without third parties listening. The Live+Giv project only
%could threaten this type by using mobile client application as trojan
%horse, collecting any communication data (chat, sms, microphone).
%
%\subparagraph{4 Privacy of Data and Image}
%
%\emph{``This type is concerned with `making sure that individuals's data
%is not automatically available to other individuals and
%organisations'\,''} \cite{1}. This is
%Informational Privacy in an intuitive sense regarding data like:
%
%\begin{itemize}
%
%\item
%  Phone Number
%\item
%  IP Address
%\item
%  Public-administrative Data (Date of Birth, population register)
%\item
%  Data held by organizations, like Banks or Insurance Companies
%\item
%  All data that is stored in online services (Facebook)
%\end{itemize}
%
%The Live+Gov project does not threaten this type directly if we assume a
%secure and closed system. However, this privacy type could be threatened
%by carelessly ignoring known (technical) vulnerabilities regarding data
%security. Additionally we could threaten the Privacy of Data and Image
%indirectly by linking collected data with other sources.
%
%\subparagraph{5 Privacy of Thoughts and Feelings}
%
%\emph{``This type is the right `not to share their thoughts or feelings
%or to have those thoughts or feeling (sic!) revealed'\,''}
%\cite{1}. This means thoughts and emotions must
%not be detected autmatically. Intuitively the Live+Gov system seems
%unable to threaten this type. However, considering the issue component
%of the Urban Maintaince use case, this might reveal information about
%one's thoughts regarding the community in a positive manner. Solely by
%taking part we could assume a caring personality. This threatens one's
%privacy in a rather technical sense, but does not necessarily impose any
%harm.
%
%An other way of threatening this type could be constructed by recording
%one's voice with the phone's microphone and run emotion detecting
%algorithms against this data.
%
%\subparagraph{6 Privacy of Location and Space}
%
%\emph{``This type is the right `to move about in public or semi-public
%space withoug being identified, tracked or monitored'. Additionally this
%type is concerned with the protection of one's home and private places
%(`right to solitude')''} \cite{1}. The location
%dimension of this type is relatively easy to understand: The
%geo-position of citizens cannot be monitored by default. However, by
%actively taking part in the Live+Gov project, the locational privacy of
%citizens is threatened by default because data of the location sensor
%will be collected. The space dimension is more complex, but can be
%simplified with a \emph{``right to solitude''}. This dimension could be
%threatend with the invasion of personal space in any means, i.e.~by
%disrespecting one's right to an inviolate home or by undercutting one's
%comfort zone in an conversation. Live+Gov only utilizes the mobile
%devices of citizens, so we could disrespect the former by activating the
%phone's micropone and start recording.
%
%\subparagraph{7 Privacy of Association}
%
%\emph{``This type is the right `to associate with whomever [one]
%wish, withoug being monitored'.''} \cite{1}. This
%means that one's associations must not be recoreded by default
%independet from any suspicion. Anyhow, it does not mean that this right
%cannot be forfeit given a reasonable suspicion. The Live+Gov project
%could easily threaten this type just by linking locational data with
%yellow pages and a map. Even if an association graph cannot be deducted
%for individual citizens, we could aggregate the data to create an
%association graph for a whole population as the Live+Gov system is
%applied to a restricted urban area.

>>>>

The Act's definition of personal data covers any data that can be used to identify a living individual.
Anonymised or aggregated data is not regulated by the Act, providing the anonymisation or aggregation has not been done in a reversible way.

@@
